---
title: "R Notebook"
output: html_notebook
---

# Dependencies

```{r}

rm(list = ls())

library(tidyverse)
library(readxl)
library(lubridate)
library(gridExtra)
library(plm)
library(lmtest)
library(estimatr)
library(miceadds)
library(multiwayvcov)
library(quantreg)
library(psych)

```

Condos data after structuring and munge (see other R Markdown file, "Condos_CLT_proj.Rmd" for more explication and codes. Note: matched neighborhoods in Excel by hand pre- and post-busing).

Saved ndf file as Rdata to avoid any chance that re-run of the last code will result in changes to this dataframe.

```{r}

load(file = "ndf.Rdata")

```

# Data clean

Need to adjust nominal dollars to real dollars (2010$).

```{r}

# Load matched sample on houses to get adjustments for real list/sales prices from nominal list/sales prices.
load(file = "matched_clt.Rdata")

# Yearly adjustments for dollars
yearly_dols_adj = matched_clt_df %>%
  mutate( daily = ymd(sold) ,
          year_fe = factor(year(daily)) ) %>%
  select( year_fe , `2010$ Rate` ) %>%
  group_by(year_fe) %>%
  summarize( adj = mean(`2010$ Rate`) )

# Merge in with condos dataframe and create variables
condos = ndf %>%
  mutate( daily = ymd(sold) ,
          new = ifelse(new_construct == "Yes" , 1 , 0) ,
          age = 2010 - year_built ,
          agesq = age^2 ,
          year_fe = factor(year(daily)) ) %>%
  left_join(yearly_dols_adj , by = "year_fe" ) %>%
  mutate( rsp = sp / adj ,
          rlp = lp / adj , 
          lrsp = log(rsp) ,
          lrlp = log(rlp) )

```

# Regression analyses

## Linear DiD models

Treatment and timing variables

```{r}

# Treatments are categorical here (0,1 and interactions) and for date sold before/after rezoning
treated_df = condos %>%
  mutate( year_fe = factor(year(daily)) ) %>% 
  # First are neighborhood treatments
  mutate( rezone = ifelse(treat == 1 | treat == 2 , 1 , 0) ) %>%
  # Next are date treatments
  mutate( post2002 = ifelse(sold < "2002-04-15", 0 , 1) ) %>%
  # Interaction of two is treatment, positive treatment, and negative treatment
  mutate( treat = rezone*post2002 )

# Positively treated dataframe
treated_pos_df = condos %>%
  filter( treat %in% c(0,1) ) %>%
  mutate( year_fe = factor(year(daily)) ) %>% 
  # First are neighborhood treatments
  mutate( rezonepos = ifelse(treat == 1 , 1 , 0) ) %>%
  # Next are date treatments
  mutate( post2002 = ifelse(sold < "2002-04-15", 0 , 1) ) %>%
  # Interaction of two is treatment, positive treatment, and negative treatment
  mutate( treatpos = rezonepos*post2002 ,
          eocptreat = eoc_diff*treatpos)

# Negatively treated dataframe
treated_neg_df = condos %>%
  filter( treat %in% c(0,2) ) %>%
  mutate( year_fe = factor(year(daily)) ) %>% 
  # First are neighborhood treatments
  mutate( rezoneneg = ifelse(treat == 2 , 1 , 0) ) %>%
  # Next are date treatments
  mutate( post2002 = ifelse(sold < "2002-04-15", 0 , 1) ) %>%
  # Interaction of two is treatment, positive treatment, and negative treatment
  mutate( treatneg = rezoneneg*post2002 ,
          eocntreat = eoc_diff*treatneg)

```

Simple first-pass regressions without hedonic covariates

```{r}

# Full treatment (aggregating both positive and negative treatment effects)
simp_reg = lm( lrsp ~ rezone + post2002 + treat , data = treated_df)
summary(simp_reg)

# Overall treatment
summary( lm_robust(lrsp ~ rezone + post2002 + treat , 
                data = treated_df , 
                se_type = "stata") )

# Positively treated 
summary( lm_robust(lrsp ~ rezonepos + post2002 + treatpos , 
                data = treated_pos_df , 
                se_type = "stata") )

# Negatively treated
summary( lm_robust(lrsp ~ rezoneneg + post2002 + treatneg , 
                data = treated_neg_df , 
                se_type = "stata") )

```

Hedonic regression results. Pared down covariates due to being condos rather than houses (some covariates do not make sense in condo context)

```{r}

# Positively treated 
summary(lm_robust(
  lrsp ~ rezonepos + post2002 + treatpos + beds + total_hla + new + age + agesq , 
                data = treated_pos_df , 
                se_type = "stata") )

# Negatively treated
summary( lm_robust(
  lrsp ~ rezoneneg + post2002 + treatneg + beds + total_hla + age + agesq , 
                data = treated_neg_df , 
                se_type = "stata") )

```

### EOC-treatment regressions

```{r}

# Positively treated base model
summary( lm_robust(lrsp ~ eoc_diff + post2002 + eocptreat, 
                data = treated_pos_df , 
                se_type = "stata") )

# Negatively treated base model
summary( lm_robust(lrsp ~ eoc_diff + post2002 + eocntreat, 
                data = treated_neg_df , 
                se_type = "stata") )

```

```{r}

# Positively treated base model
summary( lm_robust(lrsp ~ eoc_diff + post2002 + eocptreat + beds + total_hla + new + age + agesq , 
                data = treated_pos_df , 
                se_type = "stata") )

# Negatively treated base model
summary( lm_robust(lrsp ~ eoc_diff + post2002 + eocntreat + beds + total_hla + age + agesq , 
                data = treated_neg_df , 
                se_type = "stata") )

```

