---
title: "R Notebook"
output: html_notebook
---

# Dependencies

```{r}

rm(list = ls())

library(tidyverse)
library(readxl)
library(lubridate)
library(gridExtra)
library(plm)
library(lmtest)
library(estimatr)
library(miceadds)
library(multiwayvcov)
library(quantreg)
library(psych)

```

# Data clean

Data import - full Charlotte housing data

```{r}

# Import full Charlotte housing data
load(file = "full_clt.Rdata")

```

Get data from MLS on condo prices

```{r}

load("clt_condos.Rdata")

```

Keep duplicates of CMS condo prices

```{r}

condos = Full_Charlotte_HousesCondos_Data_Set %>%
  mutate( Address = str_replace_all(address , fixed(" ") , "") ,
          Address = toupper(Address) ) %>%
  group_by(Address) %>%
  filter( n() > 1 )

```



```{r}

match_data = full_clt_df %>%
  select( subdiv , treat , `EOC Difference` ) %>%
  group_by(subdiv) %>%
  summarize( treat = mean(treat) , 
             eoc_diff = mean(`EOC Difference` , na.rm = TRUE) )

condo_joined = condos %>%
  left_join(match_data , by = "subdiv")

```

Condo neighborhoods began to be recorded on 9/19/2003 (sparingly)

Seperate files into pre-neighborhood and post-neighborhood era and join on address

```{r}

no_neigh_data = condo_joined %>%
  filter(sold < "2003-09-19")

neigh_data = condo_joined %>%
  filter(sold >= "2003-09-19")

```

Join together two dataframes to get neighborhoods in

```{r}

neigh_replace = neigh_data %>%
  select(Address , subdiv) %>%
  right_join(no_neigh_data , by = "Address")

```

Examine for completeness and also to replace treatments and EOC Differences

```{r}

ndf = neigh_replace %>%
  select( -subdiv.y ) %>%
  bind_rows(neigh_data) %>%
  select( Address , subdiv.x , treat , eoc_diff , everything() ) %>%
  arrange( Address )

#write_excel_csv(ndf , "ndf.csv")

```



