---
title: "R Notebook"
output: html_notebook
---

# Dependencies

```{r}

rm(list = ls())

library(tidyverse)

```

# Data

## Data Importation

Load in data from "Disaggregated Results" into working environment - test score data

```{r}

eoc_path = "/Users/edwardhearn/Desktop/Stata Dissertation Files for Conversion to R/Charlotte House Price Project/CMS EOC Disagg Data"

eoclist = list.files(path = "CMS EOC Disagg Data" , pattern = ".*_Data.txt")

eocdata = lapply( file.path(eoc_path , eoclist) , function(x) {read.delim(x,header = TRUE,sep = "\t",dec = ".")} )

```


```{r}

nameslist = list.files(path = "CMS EOC Disagg Data" , pattern = ".*_Schools.txt")

namesdata = lapply( file.path(eoc_path , nameslist),function(x) {read.delim(x,header = TRUE,sep = "\t",dec = ".")} )


```

Add year indexing (specific dataframes from specific years)

```{r}

years = 2002:2010

for ( i in seq_along(eocdata) ) {
  eocdata[[i]]$year = rep( years[i] , nrow(eocdata[[i]]) )
}

```

Bind rows into one unified dataframe for processing

```{r}

eoc_df = do.call("rbind" , eocdata)
names_df = do.call("rbind" , namesdata)

names = names_df %>%
  group_by(school_code) %>%
  slice(n())

```

## Data Processing

```{r}

# Filter to three EOCs of interest: Algebra I (A1), Biology (BI), and English I (E1)
eoc_sub = eoc_df %>%
  filter( subject %in% c("A1" , "BI" , "E1") & subgroup == "TOT" )

```

Join together EOC data and school names

```{r}

# Filter to specific CMS high schools under study (CMS school codes begin with "600")
cms_hs = eoc_sub %>%
  left_join( names , by = "school_code" ) %>%
  filter( str_detect(school_code , "^600") & grade_span == "09-12" & assessment == "MC" ) %>%
  select( school_code , school_name , everything() )

cms_hs

```

Convert data to R format for ease/speed of coding results

```{r}

load(file = "cms_hs.Rdata")
#save(cms_hs , file = "cms_hs.Rdata")

```

Get high school score averages

```{r}

cms_hs_scores = cms_hs %>%
  select( school_code , school_name , subject , year , pct_prof , avg_score ) %>%
  mutate( pct_pass = as.character(pct_prof) , 
          pct_pass = ifelse(pct_pass == "<5" , 5 , pct_pass) ,
          pct_pass = ifelse(pct_pass == ">95", 95 , pct_pass) ,
          pct_pass = as.numeric(pct_pass) ) %>%
  mutate( school_name = as.character(school_name) ,
          school_name = ifelse( str_detect(school_name,"Olympic") , "Olympic High" , school_name) ,
          school_name = ifelse( str_detect(school_name,"Garinger") , "Garinger High" , school_name) )

cms_hs_scores %>% arrange(school_name)

```

Aggregate results to yearly composite of all three exams' passing rates per school

```{r}

# Aggregated over post-busing period
cms_hs_scores %>%
  filter(year >= 2002) %>%
  group_by(school_name) %>%
  summarize( pct_pass_composite = mean(pct_pass) )

# Aggregated over post-busing period; broken out by subject
cms_hs_scores %>%
  filter(year >= 2002) %>%
  group_by(school_name , subject) %>%
  summarize( pct_pass_composite = mean(pct_pass) )

# Yearly results
cms_hs_scores %>%
  filter(year >= 2002) %>%
  group_by(school_name , year) %>%
  summarize( pct_pass_composite = mean(pct_pass) )

```



