---
title: "Full Charlotte Data Codes"
output: html_notebook
---

# Dependencies

```{r}

rm(list = ls())

library(tidyverse)
library(readxl)
library(lubridate)
library(gridExtra)
library(plm)
library(lmtest)
library(estimatr)
library(miceadds)
library(multiwayvcov)
library(quantreg)
library(psych)

```

# Data clean

Data import - full Charlotte housing data

```{r}

# Import full Charlotte housing data
load(file = "full_clt.Rdata")

```

Examine EOC Composite scores by high school and year

```{r}

eoc = full_clt_df %>%
  mutate( year = year(sold) ) %>%
  group_by(high , year) %>%
  summarize(eoc_comp = mean(`EOC Composite`) )

eoc

```

Add a ranking variable for plotting (1997 ranks and where these go year over year)

```{r}

# Numeric rank by 1998 passing rates
eoc_ranks = eoc %>%
  filter(year == 1998) %>%
  arrange( desc(eoc_comp) )

# Sub in ranks, leaving one out for EE Waddell (2002 scores subbed for 1998)
eoc_ranks = cbind( eoc_ranks , rank = c(1:8,10:14) )

# Merge ranks in with yearly eoc pass rates by high school
eoc_rank_years = eoc_ranks %>%
  select(high , rank) %>%
  right_join( eoc , by = "high" ) %>%
  mutate( rank = ifelse(high == "E.E. Waddell" , 9 , rank) ,
          short_high = paste0(str_sub(high,1,1) , str_sub(high,-1)) )

eoc_rank_names = eoc_rank_years %>%
  filter(high != "Harding University") %>%
  group_by(year) %>%
  arrange( year , desc(eoc_comp) ) %>%
  mutate( yr_rank = rank(eoc_comp , ties.method = "first") ) %>%
  na.omit()

eoc_rank_names

```

Visualize results of EOC passing rate rankings

```{r}

png("Figures & Visuals/eoc_school_numeric_rankings.png" , width = 900 , height = 500)

plot( x = eoc_rank_years$year , y = eoc_rank_years$eoc_comp , type = "n" , xaxt = "n" ,
      xlab = "" , ylab = "EOC Passing Rate" )
text( x = jitter(eoc_rank_years$year,2) , y = eoc_rank_years$eoc_comp , 
      labels = eoc_rank_years$rank , cex = 0.8 )
axis( 1 , at = 1997:2010 , labels = FALSE , tick = FALSE)
text( x = 1997:2010 , par("usr")[3] - 0.5 , 
     labels = 1997:2010 , srt = 35 , pos = 1 , xpd = TRUE) 
for ( i in c(1997:2009) ) {
  abline( v = i + 0.5 , lty = 2 , col = "gray" )
}

dev.off()

```

Rankings by school names

```{r}

png("Figures & Visuals/eoc_school_rankings.png" , width = 900 , height = 500)

plot( x = eoc_rank_names$year , y = eoc_rank_names$yr_rank , type = "n" , xaxt = "n" , yaxt = "n" ,
      xlab = "" , ylab = " " )
text( x = eoc_rank_names$year , y = eoc_rank_names$yr_rank , 
      labels = eoc_rank_names$short_high , cex = 1 , 
      col = round(eoc_rank_names$rank^0.5,0) )
axis( 1 , at = 1997:2010 , labels = FALSE , tick = FALSE)
text( x = 1997:2010 , par("usr")[3] - 0.5 , 
     labels = 1997:2010 , srt = 35 , pos = 1 , xpd = TRUE) 

dev.off()

```

Clean and format data on Charlotte house prices - full data 

```{r}

# Filter on conditions that aren't realistic for houses in full Charlotte dataframe
full_clt = full_clt_df %>%
  rename(eoccomposite = `EOC Composite` ,
         eocdifference = `EOC Difference` ,
         half_baths = `half baths`) %>%
  mutate( daily = ymd(sold) ,
          new = ifelse(new_construct == "Yes" , 1 , 0) ,
          age = 2010 - year_built ,
          agesq = age^2 ,
          lrsp = log(rsp) ,
          lrlp = log(rlp) ) %>%
  filter( !(baths > 6) ) %>%
  filter( !(acres > 10) ) %>%
  filter( !(age < 0) ) %>%
  filter( !(age > 200) ) %>%
  filter( !(total_hla == 0) ) %>%
  filter( !(baths == 0 & half_baths == 0) ) %>%
  filter( !(baths == 0) ) %>%
  filter( !(beds < 1) ) %>%
  filter( !(rsp < 1000) ) %>%
  filter( !(treat == 1 & eocdifference < 0) ) %>%
  filter( !(treat == 2 & eocdifference > 0) ) #%>% # Comment/uncomment full data/subset data to filter new hs in cms
  #filter(daily <= "2006-08-01")

```

# DiD summary statistics

Take a look at difference-in-difference tables: 

```{r}

# Control Neighborhoods
# Pre-busing:
cpreb = c( mean(full_clt$rsp[full_clt$treat == 0 & full_clt$daily <= "2002-04-15"]) , 
           length( full_clt$rsp[full_clt$treat == 0 & full_clt$daily <= "2002-04-15"]) )
# Post-busing:
cpostb = c( mean(full_clt$rsp[full_clt$treat == 0 & full_clt$daily > "2002-04-15"]) ,
            length(full_clt$rsp[full_clt$treat == 0 & full_clt$daily > "2002-04-15"]) )

# Positively treated neighborhoods
# Pre-busing
ppreb = c( mean(full_clt$rsp[full_clt$treat == 1 & full_clt$daily <= "2002-04-15"]) , 
           length(full_clt$rsp[full_clt$treat == 1 & full_clt$daily <= "2002-04-15"]) )
# Post-busing
ppostb = c( mean(full_clt$rsp[full_clt$treat == 1 & full_clt$daily > "2002-04-15"]) , 
            length(full_clt$rsp[full_clt$treat == 1 & full_clt$daily > "2002-04-15"]) )

# Negatively treated neighborhoods
# Pre-busing
npreb = c( mean(full_clt$rsp[full_clt$treat == 2 & full_clt$daily <= "2002-04-15"]) , 
           length(full_clt$rsp[full_clt$treat == 2 & full_clt$daily <= "2002-04-15"]) )
# Post-busing
npostb = c( mean(full_clt$rsp[full_clt$treat == 2 & full_clt$daily > "2002-04-15"]) , 
            length(full_clt$rsp[full_clt$treat == 2 & full_clt$daily > "2002-04-15"]) )

```

Gather results into differences-in-differences table (with housing totals)

``` {r}

# Pre-busing tibble
pre = t( tibble(
  cpreb, 
  ppreb , 
  npreb
) )

# Post-busing tibble
post = t( tibble(
  cpostb , 
  ppostb , 
  npostb
) )

# Wrap results into data frame
DiD = data.frame( cbind(post , pre) )

# Naming conventions: rows and columns
rnames = c("control","positive","negative")

diff_in_diff = DiD %>%
  select( X1 , X3 , X2 , X4 ) %>%
  rename( post_bus_rsp = X1 , 
          pre_bus_rsp = X3 ,
          post_bus_n = X2 , 
          pre_bus_n = X4 ) %>%
  mutate( prepost_diffs = post_bus_rsp - pre_bus_rsp )

rownames(diff_in_diff) = rnames
diff_in_diff

```

# Visualizations

House prices over time

Aggregate positively and negatively treated and control groups of houses by each month during timeframe

```{r}

# Aggregate lrsp data to lrsp averages for each day during sample timeframe (positive treatment and control groups)
monthly_lrsp_pos = full_clt %>% 
  filter( treat %in% c(0,1) ) %>%
  mutate( monthly = month(daily) ,
          yearly = year(daily) ,
          yearmon = ymd(paste0(yearly,"-",monthly,"-01")) ) %>%
  group_by(yearmon , treat) %>%
  summarize( lrsp = mean(lrsp) ,
             n = n() ) 

# Aggregate lrsp data to lrsp averages for each day during sample timeframe (negative treatment and control groups)
monthly_lrsp_neg = full_clt %>% 
  filter( treat %in% c(0,2) ) %>%
  mutate( monthly = month(daily) ,
          yearly = year(daily) ,
          yearmon = ymd(paste0(yearly,"-",monthly,"-01")) ) %>%
  group_by(yearmon , treat) %>%
  summarize( lrsp = mean(lrsp) ) 

```

Visualize aggregates of positive/control and negative/control houses

``` {r}

# Visual display of daily lrsp averages over timeframe - positive treatment and control
pos = monthly_lrsp_pos %>%
  ggplot( aes(x = yearmon , y = lrsp , color = as.factor(treat)) ) + 
  geom_point() +
  theme_bw() +
  scale_x_date( breaks = scales::pretty_breaks(20) ) +
  scale_y_continuous(limits = c(11,14.5)) +
  annotate(geom = "text" , x = ymd("2008-04-17") , y = 13 , label = "Positive" , col = "#00BFC4" , size = 5) +
  annotate(geom = "text" , x = ymd("2008-04-17") , y = 12 , label = "Control" , col = "#F8766D" , size = 5) +
  theme( axis.text.x = element_text(angle = 45 , hjust = 1) ,
         legend.position = "n" ,
         panel.grid = element_blank() ,
         axis.text=element_text(size=14) ,
         axis.title=element_text(size=14,face="bold") ) +
  labs( x = "" ,
        y = "ln(real sale price)" ,
        color = "" ,
        title = "Positively Treated vs Control Houses") +
  geom_vline(xintercept = ymd("2002-04-01") , col = "gray" , lty = 2) +
  annotate( "text" , x = ymd("2003-01-01") , y = 14.5 , label = "04/15/2002" , col = "gray" , size = 5)

# Visual display of daily lrsp averages over timeframe - negative treatment and control
neg = monthly_lrsp_neg %>%
  ggplot( aes(x = yearmon , y = lrsp , color = as.factor(treat)) ) + 
  geom_point() +
  theme_bw() +
  scale_x_date( breaks = scales::pretty_breaks(20) ) +
  scale_y_continuous(limits = c(11,14.5)) +
  annotate(geom = "text" , x = ymd("2007-04-17") , y = 13 , label = "Control" , col = "#F8766D" , size = 5) +
  annotate(geom = "text" , x = ymd("2007-04-17") , y = 11.7 , label = "Negative" , col = "#00BFC4" , size = 5) +
  theme( axis.text.x = element_text(angle = 45, hjust = 1) ,
         legend.position = "n" ,
         panel.grid = element_blank() ,
         axis.text=element_text(size=14) ,
         axis.title=element_text(size=14,face="bold") ) +
  labs( x = "" ,
        y = "ln(real sale price)" ,
        color = "" ,
        title = "Negatively Treated vs Control Houses") +
  geom_vline(xintercept = ymd("2002-04-01") , col = "gray" , lty = 2) +
  annotate( "text" , x = ymd("2003-01-01") , y = 14.5 , label = "04/15/2002" , col = "gray" , size = 5)

png("pos_house_price_plots.png" , width = 900 , height = 500)
pos
dev.off()

png("neg_house_price_plots.png" , width = 900 , height = 500)
neg
dev.off()

```

Plot simple month-over-month trend lines and overlay on to plot

``` {r}

# Visual display of daily lrsp averages over timeframe - positive treatment and control
pos = monthly_lrsp_pos %>%
  ggplot( aes(x = yearmon , y = lrsp , color = factor(treat)) ) + 
  geom_point(alpha = 0.3) +  
  geom_smooth( data = subset(monthly_lrsp_pos , yearmon < "2002-05-01") ,
               aes( x = yearmon , y = lrsp , color = factor(treat) ) , method = lm , se = FALSE ) +
  geom_smooth( data = subset(monthly_lrsp_pos , yearmon >= "2002-05-01") ,
               aes( x = yearmon , y = lrsp , color = factor(treat) ) , method = lm , se = FALSE ) +
  theme_bw() +
  scale_x_date( breaks = scales::pretty_breaks(20) ) +
  scale_y_continuous(limits = c(11,14.5)) +
  annotate(geom = "text" , x = ymd("2008-04-17") , y = 13 , label = "Positive" , col = "#00BFC4" , size = 5) +
  annotate(geom = "text" , x = ymd("2008-04-17") , y = 12 , label = "Control" , col = "#F8766D" , size = 5) +
  theme( axis.text.x = element_text(angle = 45, hjust = 1) ,
         legend.position = "n" ,
         panel.grid = element_blank() ,
         axis.text=element_text(size=14),
         axis.title=element_text(size=14,face="bold") ) +
  labs( x = "" ,
        y = "ln(real sale price)" ,
        color = "" ,
        title = "") +
  geom_vline(xintercept = ymd("2002-04-01") , col = "gray" , lty = 2) +
  annotate( "text" , x = ymd("2003-01-01") , y = 14.5 , label = "04/15/2002" , col = "gray" , size = 5)

# Visual display of daily lrsp averages over timeframe - negative treatment and control
neg = monthly_lrsp_neg %>%
  ggplot( aes(x = yearmon , y = lrsp , color = as.factor(treat)) ) + 
  geom_point(alpha = 0.3) +
  theme_bw() +
  geom_smooth( data = subset(monthly_lrsp_neg , yearmon < "2002-05-01") ,
               aes( x = yearmon , y = lrsp , color = factor(treat) ) , method = lm , se = FALSE ) +
  geom_smooth( data = subset(monthly_lrsp_neg , yearmon >= "2002-05-01") ,
               aes( x = yearmon , y = lrsp , color = factor(treat) ) , method = lm , se = FALSE ) +
  scale_x_date( breaks = scales::pretty_breaks(20) ) +
  scale_y_continuous(limits = c(11,14.5)) +
  annotate(geom = "text" , x = ymd("2007-04-17") , y = 13 , label = "Control" , col = "#F8766D" , size = 5) +
  annotate(geom = "text" , x = ymd("2007-04-17") , y = 11.7 , label = "Negative" , col = "#00BFC4" , size = 5) +
  theme( axis.text.x = element_text(angle = 45, hjust = 1) ,
         legend.position = "n" ,
         panel.grid = element_blank() ,
         axis.text=element_text(size=14),
         axis.title=element_text(size=14,face="bold") ) +
  labs( x = "" ,
        y = "ln(real sale price)" ,
        color = "" ,
        title = "") +
  geom_vline(xintercept = ymd("2002-04-01") , col = "gray" , lty = 2) +
  annotate( "text" , x = ymd("2003-01-01") , y = 14.5 , label = "04/15/2002" , col = "gray" , size = 5 )

png("pos_house_price_trends.png" , width = 900 , height = 500)
pos
dev.off()

png("neg_house_price_trends.png" , width = 900 , height = 500)
neg
dev.off()

```

Notes: 

- Data issues from MLS in late 1999 to early 2001 obfuscate empirical trend lines and house prices (average monthly house prices during this period calculated from small numbers of house sales, sometimes 1, 2, 3. Some months have no house sales). Had this data not been lost, would have seen sharper patterns and likely closer trend lines without such a disparate drop down. Story here is in the slopes, not the immediate effects! (Lottery offset these)

- Trends essentially parallel in positive/control pre-busing period; clear change in trends afterward, with positive control group of neighborhood-houses continuing upward trajectory, while control switch tack. Also, large drop-down relative to positively treated neighborhoods indicates bigger negative effect at first and then substantial on-going effects from change in school assignment policy. People bidding up house prices in these areas relative to control houses (which are fall in house price post-busing).

- Negative trends tell another side of the story: no immediate effects for negatiely treated houses relative to controls; negative slope didn't change much either. Control slope, as before, is (would be less) slightly positive until busing decision, then gradually negative afterward. Negative prices bid down slightly faster in post-busing era. 

# Regression analyses

Linear models encapsulate both dummy-treatment and EOC-difference treatment.

Set up variables for treatment and control groups (positively and negatively treated). This requires dummies for treated (positively and negatively) and date sold (pre- and post-April 15, 2002).

```{r}

# Treatments are categorical here (0,1 and interactions) and for date sold before/after rezoning
treated_df = full_clt %>%
  mutate( year_fe = factor(year(daily)) ) %>% 
  # First are neighborhood treatments
  mutate( rezone = ifelse(treat == 1 | treat == 2 , 1 , 0) ) %>%
  # Next are date treatments
  mutate( post2002 = ifelse(sold < "2002-04-15", 0 , 1) ) %>%
  # Interaction of two is treatment, positive treatment, and negative treatment
  mutate( treat = rezone*post2002 )

# Positively treated dataframe
treated_pos_df = full_clt %>%
  filter( treat %in% c(0,1) ) %>%
  mutate( year_fe = factor(year(daily)) ) %>% 
  # First are neighborhood treatments
  mutate( rezonepos = ifelse(treat == 1 , 1 , 0) ) %>%
  # Next are date treatments
  mutate( post2002 = ifelse(sold < "2002-04-15", 0 , 1) ) %>%
  # Interaction of two is treatment, positive treatment, and negative treatment
  mutate( treatpos = rezonepos*post2002 ,
          eocptreat = eocdifference*treatpos)

# Negatively treated dataframe
treated_neg_df = full_clt %>%
  filter( treat %in% c(0,2) ) %>%
  mutate( year_fe = factor(year(daily)) ) %>% 
  # First are neighborhood treatments
  mutate( rezoneneg = ifelse(treat == 2 , 1 , 0) ) %>%
  # Next are date treatments
  mutate( post2002 = ifelse(sold < "2002-04-15", 0 , 1) ) %>%
  # Interaction of two is treatment, positive treatment, and negative treatment
  mutate( treatneg = rezoneneg*post2002 ,
          eocntreat = eocdifference*treatneg)

```

## Validation measure: logistic regression

Logistic regression of whether school board assigned worse performing schools into treated neighborhoods

```{r}

treat_df = treated_df %>%
  mutate(treat = rezone*post2002)

# Total treated
(mod_logit = summary(glm( treat ~ scale(SAT) + scale(eoccomposite) + scale(TEOC) , data = treat_df , family = binomial(link = "logit") )))
# MFX
for (i in 2:4) {
  print( arm::invlogit(mod_logit$coefficients[1] + mod_logit$coefficients[i]) - arm::invlogit(mod_logit$coefficients[1]) )
}

# Positively treated
(mod_logit_pos = summary(glm( treatpos ~ scale(SAT) + scale(eoccomposite) + scale(TEOC) , data = treated_pos_df , family = binomial(link = "logit") )))
# MFX
for (i in 2:4) {
  print( arm::invlogit(mod_logit_pos$coefficients[1] + mod_logit_pos$coefficients[i]) - arm::invlogit(mod_logit_pos$coefficients[1]) )
}

# Negatively treated
(mod_logit_neg = summary(glm( treatneg ~ scale(SAT) + scale(eoccomposite) + scale(TEOC) , data = treated_neg_df , family = binomial(link = "logit") )))
# MFX
for (i in 2:4) {
  print( arm::invlogit(mod_logit_neg$coefficients[1] + mod_logit_neg$coefficients[i]) - arm::invlogit(mod_logit_neg$coefficients[1]) )
}

```

Aggregate scores and standard deviations on measures above.

```{r}

mean(treated_pos_df$eoccomposite , na.rm = TRUE)
mean(treated_pos_df$SAT , na.rm = TRUE)
mean(treated_pos_df$TEOC , na.rm = TRUE)

sd(treated_pos_df$eoccomposite , na.rm = TRUE)
sd(treated_pos_df$SAT , na.rm = TRUE)
sd(treated_pos_df$TEOC , na.rm = TRUE)

```

## Linear DiD models

Simple first-pass regressions without hedonic covariates

```{r}

# Full treatment (aggregating both positive and negative treatment effects)
simp_reg = lm( lrsp ~ rezone + post2002 + treat , data = treated_df)
summary(simp_reg)

# Overall treatment
summary( lm_robust(lrsp ~ rezone + post2002 + treat , 
                data = treated_df , 
                se_type = "stata" ,
                clusters = treated_df$subdiv) )

# Positively treated 
summary( lm_robust(lrsp ~ rezonepos + post2002 + treatpos , 
                data = treated_pos_df , 
                se_type = "stata" ,
                clusters = treated_pos_df$subdiv) )

# Negatively treated
summary( lm_robust(lrsp ~ rezoneneg + post2002 + treatneg , 
                data = treated_neg_df , 
                se_type = "stata" ,
                clusters = treated_neg_df$subdiv) )

```

Incorporate hedonic variables into the analyses

```{r}

# Overall treatment
summary( lm_robust(
  lrsp ~ rezone + post2002 + treat + acres + beds + baths + half_baths + new + age + agesq + year_fe , 
                data = treated_df ,
                se_type = "stata" ,
                clusters = treated_df$subdiv) )

# Treatment-by-year
summary( lm_robust(
  lrsp ~ rezone + acres + beds + baths + half_baths + new + age + agesq + year_fe + year_fe*rezone , 
                data = treated_df ,
                se_type = "stata" ,
                clusters = treated_df$subdiv) )

```

Positive treatment regression results by total and year-over-year

```{r}

# Positively treated 
summary(lm_robust(
  lrsp ~ rezonepos + post2002 + treatpos + acres + beds + baths + half_baths + new + age + agesq + year_fe , 
                data = treated_pos_df , 
                se_type = "stata" ,
                clusters = treated_pos_df$subdiv) )

# Year-over-year
summary(lm_robust(
  lrsp ~ rezonepos + acres + beds + baths + half_baths + new + age + agesq + year_fe + year_fe*rezonepos , 
                data = treated_pos_df , 
                se_type = "stata" ,
                clusters = treated_pos_df$subdiv) )

```

Negative treatment regression results by total and year-over-year

``` {r}

# Negatively treated
summary( lm_robust(
  lrsp ~ rezoneneg + post2002 + treatneg + acres + beds + baths + half_baths + new + age + agesq + year_fe , 
                data = treated_neg_df , 
                se_type = "stata" ,
                clusters = treated_neg_df$subdiv) )

# Year-over-year
summary( lm_robust(
  lrsp ~ rezoneneg + acres + beds + baths + half_baths + new + age + agesq + year_fe + rezoneneg*year_fe , 
                data = treated_neg_df , 
                se_type = "stata" ,
                clusters = treated_neg_df$subdiv) )

```

Incorporate EOC-difference (or "doseage") model for houses in neighborhoods that experienced positive and negative treatment effects of a school reassignment: base models

```{r}

# Positively treated base model
summary( lm_robust(lrsp ~ eocdifference + post2002 + eocptreat, 
                data = treated_pos_df , 
                se_type = "stata" ,
                clusters = treated_pos_df$subdiv) )

# Year-over-year base model
summary( lm_robust(lrsp ~ eocdifference + year_fe + eocdifference*year_fe, 
                data = treated_pos_df , 
                se_type = "stata" ,
                clusters = treated_pos_df$subdiv) )

# Negatively treated base model
summary( lm_robust(lrsp ~ eocdifference + post2002 + eocntreat, 
                data = treated_neg_df , 
                se_type = "stata" ,
                clusters = treated_neg_df$subdiv) )

# Year-over-year base model
summary( lm_robust(lrsp ~ eocdifference + post2002 + eocntreat, 
                data = treated_neg_df , 
                se_type = "stata" ,
                clusters = treated_neg_df$subdiv) )

```

Hedonic house attributes models: EOC-difference treatments

```{r}

# Positively treated EOC-difference
summary(lm_robust(
  lrsp ~ eocdifference + post2002 + eocptreat + acres + beds + baths + half_baths + new + age + agesq + year_fe , 
                data = treated_pos_df , 
                se_type = "stata" ,
                clusters = treated_pos_df$subdiv) )

# Year-over-year EOC-difference
pos_yearly = lm_robust(
  lrsp ~ eocdifference + acres + beds + baths + half_baths + new + age + agesq + year_fe + eocdifference*year_fe , 
                data = treated_pos_df , 
                se_type = "stata" ,
                clusters = treated_pos_df$subdiv)

# Negatively treated EOC-difference
summary( lm_robust(
  lrsp ~ eocdifference + post2002 + eocntreat + acres + beds + baths + half_baths + new + age + agesq + year_fe , 
                data = treated_neg_df , 
                se_type = "stata" ,
                clusters = treated_neg_df$subdiv) )

# Year-over-year EOC-difference
neg_yearly = lm_robust(
  lrsp ~ eocdifference + acres + beds + baths + half_baths + new + age + agesq + year_fe + eocdifference*year_fe , 
                data = treated_neg_df , 
                se_type = "stata" ,
                clusters = treated_neg_df$subdiv)

```

Delineate variables needed for plotting

```{r}

# Positive/negative treatment effects
yfx_pos = pos_yearly$coefficients[23:length(pos_yearly$coefficients)]
yfx_neg = neg_yearly$coefficients[23:length(neg_yearly$coefficients)]

# Positive/negative standard errors
sefx_pos = pos_yearly$std.error[23:length(pos_yearly$std.error)]
sefx_neg = neg_yearly$std.error[23:length(neg_yearly$std.error)]

# Years
years = 1998:2010

```

Positive-treatment yearly effects plot with CI bars

``` {r}

png("pos_fx_yearly.png" , width = 900 , height = 500)

# Delineate tick marks for years
xtick = 1998:2010

# Plot of yearly effects with 2 SE (95% CI) bars
plot( y = yfx_pos , x = years , type = "b" , pch = 16 , ylim = c(-.05,.02) , xaxt = "n" , 
xlab = "" , ylab = "Estimate" , main = "Positive Treatment Coefficient Estimates: EOC Differences" , 
las = 1 , mgp = c(3.3,1,0) )
axis( 1 , at = 1998:2010 , labels = FALSE )
text( x = xtick , par("usr")[3] - 0.004 , 
     labels = xtick , srt = 35 , pos = 1 , xpd = TRUE) 
for ( i in 1:length(years) ) {
  ci = yfx_pos[i] + c(-2,2)*sefx_pos[i]
  x = years[i]
  lines( c(x,x) , ci )
}
abline( h = 0 )
abline( v = 2002+(105/365) , lty = 2 , col = "gray" )
text( x = 2003 , y = .02 , labels = "4/15/2002" , col = "gray" )

dev.off()

```

Negative-treatment yearly effects plot with CI bars

```{r}

png("neg_fx_yearly.png" , width = 900 , height = 500)

# Delineate tick marks for years
xtick = 1998:2010

# Plot of yearly effects with 2 SE (95% CI) bars
plot( y = yfx_neg , x = years , type = "b" , ylim = c(-.03,.01) , pch = 16 , xaxt = "n" , 
      xlab = "" , main = "Negative Treatment Coefficient Estimates: EOC Differences" , ylab = "Estimate" ,
      las = 1 , mgp = c(3.3,1,0) )
axis(1 , at = 1998:2010 , labels = FALSE)
text(x = xtick,  par("usr")[3] - 0.002, 
     labels = xtick, srt = 35, pos = 1, xpd = TRUE)
for ( i in 1:length(years) ) {
  ci = yfx_neg[i] + c(-2,2)*sefx_neg[i]
  x = years[i]
  lines( c(x,x) , ci )
}
abline( h = 0 )
abline( v = 2002+(105/365) , lty = 2 , col = "gray" )
text( x = 2003 , y = .01 , labels = "4/15/2002" , col = "gray") 

dev.off()

```

## Regressions by EOC quantiles

Quantiles of EOC differences

```{r}

# Postively treated EOC-difference quantiles
quantile( treated_pos_df$eocptreat[treated_pos_df$eocptreat != 0] , 
          probs = c(.25 , .50 , .75) , 
          na.rm = TRUE )

# Negatively treated EOC-difference quantiles
quantile( treated_neg_df$eocntreat[treated_neg_df$eocntreat != 0] , 
          probs = c(.25 , .50 , .75) , 
          na.rm = TRUE )

```

Apply same models to treatment quantiles (break treatment into bottom 25%, middle 50%, and top 25% of EOC difference totals)

Positive model results: EOC quantiles

```{r}

# Positively treated houses quantiles of EOC-difference scores
quant_pos_df = treated_pos_df %>%
  mutate( eocp25 = ifelse(eocdifference != 0 & eocdifference <= 6.93 , 1 , 0) ,
          eocp50 = ifelse(6.93 < eocdifference & eocdifference < 32.3 , 1 , 0) ,
          eocp75 = ifelse(32.3 <= eocdifference , 1 , 0) )

# Bottom 25% of EOC differences
quant_pos_25 = quant_pos_df %>%
  filter( eocp25 == 1 | eocdifference == 0 )

# Middle 50% of EOC differences
quant_pos_50 = quant_pos_df %>%
  filter( eocp50 == 1 | eocdifference == 0 )

# Upper 25% of EOC differences
quant_pos_75 = quant_pos_df %>%
  filter( eocp75 == 1 | eocdifference == 0 )

# Linear model incorporating all three treatment effects

# Bottom 25%
summary(lm_robust(
  lrsp ~ eocdifference + post2002 + eocptreat + acres + beds + baths + half_baths + new + age + agesq + year_fe , 
                data = quant_pos_25 , 
                se_type = "stata" ,
                clusters = quant_pos_25$subdiv) )

# Middle 50%
summary(lm_robust(
  lrsp ~ eocdifference + post2002 + eocptreat + acres + beds + baths + half_baths + new + age + agesq + year_fe , 
                data = quant_pos_50 , 
                se_type = "stata" ,
                clusters = quant_pos_50$subdiv) )

# Upper 75%
summary(lm_robust(
  lrsp ~ eocdifference + post2002 + eocptreat + acres + beds + baths + half_baths + new + age + agesq + year_fe , 
                data = quant_pos_75 , 
                se_type = "stata" ,
                clusters = quant_pos_75$subdiv) )

```

Negative model results: EOC quantiles

```{r}

# Positively treated houses quantiles of EOC-difference scores
quant_neg_df = treated_neg_df %>%
  mutate( eocn25 = ifelse(eocdifference != 0 & eocdifference <= -19.83 , 1 , 0) ,
          eocn50 = ifelse(-3.16 > eocdifference & eocdifference > -19.83 , 1 , 0) ,
          eocn75 = ifelse( -3.16 <= eocdifference , 1 , 0) )

# Bottom 25% of EOC differences
quant_neg_25 = quant_neg_df %>%
  filter( eocn25 == 1 | eocdifference == 0 )

# Middle 50% of EOC differences
quant_neg_50 = quant_neg_df %>%
  filter( eocn50 == 1 | eocdifference == 0 )

# Upper 25% of EOC differences
quant_neg_75 = quant_neg_df %>%
  filter( eocn75 == 1 | eocdifference == 0 )

# Linear model incorporating all three treatment effects

# Bottom 25%
summary(lm_robust(
  lrsp ~ eocdifference + post2002 + eocntreat + acres + beds + baths + half_baths + new + age + agesq + year_fe , 
                data = quant_neg_25 , 
                se_type = "stata" ,
                clusters = quant_neg_25$subdiv) )

# Middle 50%
summary(lm_robust(
  lrsp ~ eocdifference + post2002 + eocntreat + acres + beds + baths + half_baths + new + age + agesq + year_fe , 
                data = quant_neg_50 , 
                se_type = "stata" ,
                clusters = quant_neg_50$subdiv) )

# Upper 75%
summary(lm_robust(
  lrsp ~ eocdifference + post2002 + eocntreat + acres + beds + baths + half_baths + new + age + agesq + year_fe , 
                data = quant_neg_75 , 
                se_type = "stata" ,
                clusters = quant_neg_75$subdiv) )

```

## Quantile regressions across house-price distribution

Positively treated houses across 10% quantiles of house-price distribution

```{r}

quant_pos = rq( 
  lrsp ~ rezonepos + post2002 + treatpos + acres + beds + baths + half_baths + new + age + agesq + year_fe ,
  data = treated_pos_df , 
  tau = seq(.1,.9,by=.1) )

quant_pos

```

Boostrap neighborhood-clustered standard errors across quantile regressions

```{r}

# # Specify neighborhood clusters
# neigh_clust = as.factor(treated_pos_df$subdiv[-1])
# 
# # Specify quantiles 
# quants = seq(0.1 , 0.9 , by = 0.1)
# 
# # Calculate CI bands and store in empty array
# qr_array = array(NA , c(nrow = length(quants) , ncol = 2))
# 
# for ( i in 1:length(quants) ) {
#   qr_b = boot.rq(x = quant_pos$x , y = quant_pos$y , tau = quants[i] , R = 500 , cluster = neigh_clust)
#   qr_array[i,] = quantile(qr_b$B[,4] , probs = c(.025,.975) )
# }

```

Plot quantile regression results with 95% bootstrapped and neighborhood-clustered CIs

```{r}

# # Plot results and 95% clustered, bootstrap CIs
# plot(quant_pos$coefficients[4,] , ylim = range(qr_array) , pch = 16 , xaxt = "n" ,
#      ylab = "Coefficient estimate" , xlab = "Quantile" , main = "Positively Treated House Price Effects: Quantile Regressions")
# axis(1 , at = seq(1,9,by=1) , labels = seq(.1,.9,by=.1))
# lines(qr_array[,1] , lty = 2)
# lines(qr_array[,2] , lty = 2)
# abline(h = 0)

```

Negatively treated houses across 10% quantiles of house price distribution

```{r}

quant_neg = rq( 
  lrsp ~ rezoneneg + post2002 + treatneg + acres + beds + baths + half_baths + new + age + agesq + year_fe ,
  data = treated_neg_df , 
  tau = seq(.1,.9,by=.1) )

quant_neg

```

Boostrap neighborhood-clustered standard errors across quantile regressions

```{r}

# # Specify neighborhood clusters
# neigh_clust = as.factor(treated_neg_df$subdiv[-1])
# 
# # Specify quantiles 
# quants = seq(0.1 , 0.9 , by = 0.1)
# 
# # Calculate CI bands and store in empty array
# qr_array = array(NA , c(nrow = length(quants) , ncol = 2))
# 
# for ( i in 1:length(quants) ) {
#   qr_b = boot.rq(x = quant_neg$x , y = quant_neg$y , tau = quants[i] , R = 500 , cluster = neigh_clust)
#   qr_array[i,] = quantile(qr_b$B[,4] , probs = c(.025,.975) )
# }

```

Plot quantile regression results with 95% bootstrapped and neighborhood-clustered CIs

```{r}

# plot(quant_neg$coefficients[4,] , ylim = range(qr_array) , pch = 16 , xaxt = "n" ,
#      ylab = "Coefficient estimate" , xlab = "Quantile" , main = "Negatively Treated House Price Effects: Quantile Regressions")
# axis(1 , at = seq(1,9,by=1) , labels = seq(.1,.9,by=.1))
# lines(qr_array[,1] , lty = 2)
# lines(qr_array[,2] , lty = 2)
# abline(h = 0)

```


```{r}

describe(full_clt)
describe(treated_df$eocdifference[treated_df$eocdifference != 0])
describe(treated_pos_df$eocdifference[treated_pos_df$treat == 1])
describe(treated_neg_df$eocdifference[treated_neg_df$treat == 2])

```

