---
title: "Matched Charlotte Data Codes"
output: html_notebook
---

# Dependencies

```{r}

rm(list = ls())

library(tidyverse)
library(readxl)
library(lubridate)
library(gridExtra)
library(plm)
library(lmtest)
library(estimatr)
library(miceadds)
library(multiwayvcov)
library(quantreg)

```

# Data clean

Data import - matched Charlotte housing data

```{r}

# Import matched Charlotte housing data
load(file = "matched_clt.Rdata")

```

Clean and format data on Charlotte house prices - matched address data 

```{r}

# Filter on conditions that aren't realistic for houses in full Charlotte dataframe
matched_clt = matched_clt_df %>%
  rename(eoccomposite = `EOC Composite` ,
         eocdifference = `EOC Difference` ,
         half_baths = `half baths`) %>%
  mutate( daily = ymd(sold) ,
          new = ifelse(new_construct == "Yes" , 1 , 0) ,
          age = 2010 - year_built ,
          agesq = age^2 ,
          lrsp = log(rsp) ,
          lrlp = log(rlp) ) %>%
  filter( !(baths > 6) ) %>%
  filter( !(acres > 10) ) %>%
  filter( !(age < 0) ) %>%
  filter( !(age > 200) ) %>%
  filter( !(total_hla == 0) ) %>%
  filter( !(baths == 0 & half_baths == 0) ) %>%
  filter( !(baths == 0) ) %>%
  filter( !(beds < 1) ) %>%
  filter( !(rsp < 1000) ) %>%
  filter( !(treat == 1 & eocdifference < 0) ) %>%
  filter( !(treat == 2 & eocdifference > 0) ) #%>% # Comment/uncomment full data/subset data to filter new hs in cms
  #filter(daily <= "2006-08-01")

```

# Regression analyses

## Linear DiD models

Linear models encapsulate both dummy-treatment and EOC-difference treatment.

Set up variables for treatment and control groups (positively and negatively treated). This requires dummies for treated (positively and negatively) and date sold (pre- and post-April 15, 2002).

```{r}

# Treatments are categorical here (0,1 and interactions) and for date sold before/after rezoning
treated_df = matched_clt %>%
  mutate( year_fe = factor(year(daily)) ) %>% 
  # First are neighborhood treatments
  mutate( rezone = ifelse(treat == 1 | treat == 2 , 1 , 0) ) %>%
  # Next are date treatments
  mutate( post2002 = ifelse(sold < "2002-04-15", 0 , 1) ) %>%
  # Interaction of two is treatment, positive treatment, and negative treatment
  mutate( treat = rezone*post2002 )

# Positively treated dataframe
treated_pos_df = matched_clt %>%
  filter( treat %in% c(0,1) ) %>%
  mutate( year_fe = factor(year(daily)) ) %>% 
  # First are neighborhood treatments
  mutate( rezonepos = ifelse(treat == 1 , 1 , 0) ) %>%
  # Next are date treatments
  mutate( post2002 = ifelse(sold < "2002-04-15", 0 , 1) ) %>%
  # Interaction of two is treatment, positive treatment, and negative treatment
  mutate( treatpos = rezonepos*post2002 ,
          eocptreat = eocdifference*treatpos)

# Negatively treated dataframe
treated_neg_df = matched_clt %>%
  filter( treat %in% c(0,2) ) %>%
  mutate( year_fe = factor(year(daily)) ) %>% 
  # First are neighborhood treatments
  mutate( rezoneneg = ifelse(treat == 2 , 1 , 0) ) %>%
  # Next are date treatments
  mutate( post2002 = ifelse(sold < "2002-04-15", 0 , 1) ) %>%
  # Interaction of two is treatment, positive treatment, and negative treatment
  mutate( treatneg = rezoneneg*post2002 ,
          eocntreat = eocdifference*treatneg)

```

Simple first-pass regressions without hedonic covariates

```{r}

# Full treatment (aggregating both positive and negative treatment effects)
simp_reg = lm( lrsp ~ rezone + post2002 + treat , data = treated_df)
summary(simp_reg)

# Overall treatment
summary( lm_robust(lrsp ~ rezone + post2002 + treat , 
                data = treated_df , 
                se_type = "stata") )

# Positively treated 
summary( lm_robust(lrsp ~ rezonepos + post2002 + treatpos , 
                data = treated_pos_df , 
                se_type = "stata") )

# Negatively treated
summary( lm_robust(lrsp ~ rezoneneg + post2002 + treatneg , 
                data = treated_neg_df , 
                se_type = "stata") )

```

Incorporate hedonic variables into the analyses

```{r}

# Overall treatment
summary( lm_robust(
  lrsp ~ rezone + post2002 + treat + acres + beds + baths + half_baths + new + age + agesq + year_fe , 
                data = treated_df ,
                se_type = "stata") )

# Treatment-by-year
summary( lm_robust(
  lrsp ~ rezone + acres + beds + baths + half_baths + new + age + agesq + year_fe + year_fe*rezone , 
                data = treated_df ,
                se_type = "stata") )

```

Positive treatment regression results by total and year-over-year

```{r}

# Positively treated 
summary(lm_robust(
  lrsp ~ rezonepos + post2002 + treatpos + acres + beds + baths + half_baths + new + age + agesq + year_fe , 
                data = treated_pos_df , 
                se_type = "stata") )

# Year-over-year
summary(lm_robust(
  lrsp ~ rezonepos + acres + beds + baths + half_baths + new + age + agesq + year_fe + year_fe*rezonepos , 
                data = treated_pos_df , 
                se_type = "stata") )

```

Negative treatment regression results by total and year-over-year

``` {r}

# Negatively treated
summary( lm_robust(
  lrsp ~ rezoneneg + post2002 + treatneg + acres + beds + baths + half_baths + new + age + agesq + year_fe , 
                data = treated_neg_df , 
                se_type = "stata") )

# Year-over-year
summary( lm_robust(
  lrsp ~ rezoneneg + acres + beds + baths + half_baths + new + age + agesq + year_fe + rezoneneg*year_fe , 
                data = treated_neg_df , 
                se_type = "stata") )

```

Incorporate EOC-difference (or "doseage") model for houses in neighborhoods that experienced positive and negative treatment effects of a school reassignment: base models

```{r}

# Positively treated base model
summary( lm_robust(lrsp ~ eocdifference + post2002 + eocptreat, 
                data = treated_pos_df , 
                se_type = "stata") )

# Year-over-year base model
summary( lm_robust(lrsp ~ eocdifference + year_fe + eocdifference*year_fe, 
                data = treated_pos_df , 
                se_type = "stata") )

# Negatively treated base model
summary( lm_robust(lrsp ~ eocdifference + post2002 + eocntreat, 
                data = treated_neg_df , 
                se_type = "stata") )

# Year-over-year base model
summary( lm_robust(lrsp ~ eocdifference + post2002 + eocdifference*year_fe, 
                data = treated_neg_df , 
                se_type = "stata") )

```

Hedonic house attributes models: EOC-difference treatments

```{r}

# Positively treated EOC-difference
summary(lm_robust(
  lrsp ~ eocdifference + post2002 + eocptreat + acres + beds + baths + half_baths + new + age + agesq + year_fe , 
                data = treated_pos_df , 
                se_type = "stata") )

# Year-over-year EOC-difference
pos_yearly = lm_robust(
  lrsp ~ eocdifference + acres + beds + baths + half_baths + new + age + agesq + year_fe + eocdifference*year_fe , 
                data = treated_pos_df , 
                se_type = "stata")

# Negatively treated EOC-difference
summary( lm_robust(
  lrsp ~ eocdifference + post2002 + eocntreat + acres + beds + baths + half_baths + new + age + agesq + year_fe , 
                data = treated_neg_df , 
                se_type = "stata") )

# Year-over-year EOC-difference
neg_yearly = lm_robust(
  lrsp ~ eocdifference + acres + beds + baths + half_baths + new + age + agesq + year_fe + eocdifference*year_fe , 
                data = treated_neg_df , 
                se_type = "stata")

```

## Regressions by EOC quantiles

Quantiles of EOC differences

```{r}

# Postively treated EOC-difference quantiles
quantile( treated_pos_df$eocptreat[treated_pos_df$eocptreat != 0] , 
          probs = c(.25 , .50 , .75) , 
          na.rm = TRUE )

# Negatively treated EOC-difference quantiles
quantile( treated_neg_df$eocntreat[treated_neg_df$eocntreat != 0] , 
          probs = c(.25 , .50 , .75) , 
          na.rm = TRUE )

```

Apply same models to treatment quantiles (break treatment into bottom 25%, middle 50%, and top 25% of EOC difference totals)

Positive model results: EOC quantiles

```{r}

# Positively treated houses quantiles of EOC-difference scores
quant_pos_df = treated_pos_df %>%
  mutate( eocp25 = ifelse(eocdifference != 0 & eocdifference <= 6.93 , 1 , 0) ,
          eocp50 = ifelse(6.93 < eocdifference & eocdifference < 32.3 , 1 , 0) ,
          eocp75 = ifelse(32.3 <= eocdifference , 1 , 0) )

# Bottom 25% of EOC differences
quant_pos_25 = quant_pos_df %>%
  filter( eocp25 == 1 | eocdifference == 0 )

# Middle 50% of EOC differences
quant_pos_50 = quant_pos_df %>%
  filter( eocp50 == 1 | eocdifference == 0 )

# Upper 25% of EOC differences
quant_pos_75 = quant_pos_df %>%
  filter( eocp75 == 1 | eocdifference == 0 )

# Linear model incorporating all three treatment effects

# Bottom 25%
summary(lm_robust(
  lrsp ~ eocdifference + post2002 + eocptreat + acres + beds + baths + half_baths + new + age + agesq + year_fe , 
                data = quant_pos_25 , 
                se_type = "stata") )

# Middle 50%
summary(lm_robust(
  lrsp ~ eocdifference + post2002 + eocptreat + acres + beds + baths + half_baths + new + age + agesq + year_fe , 
                data = quant_pos_50 , 
                se_type = "stata") )

# Upper 75%
summary(lm_robust(
  lrsp ~ eocdifference + post2002 + eocptreat + acres + beds + baths + half_baths + new + age + agesq + year_fe , 
                data = quant_pos_75 , 
                se_type = "stata") )

```

Negative model results: EOC quantiles

```{r}

# Positively treated houses quantiles of EOC-difference scores
quant_neg_df = treated_neg_df %>%
  mutate( eocn25 = ifelse(eocdifference != 0 & eocdifference <= -9.97 , 1 , 0) ,
          eocn50 = ifelse(-3.19 > eocdifference & eocdifference > -9.97 , 1 , 0) ,
          eocn75 = ifelse( -3.19 <= eocdifference , 1 , 0) )

# Bottom 25% of EOC differences
quant_neg_25 = quant_neg_df %>%
  filter( eocn25 == 1 | eocdifference == 0 )

# Middle 50% of EOC differences
quant_neg_50 = quant_neg_df %>%
  filter( eocn50 == 1 | eocdifference == 0 )

# Upper 25% of EOC differences
quant_neg_75 = quant_neg_df %>%
  filter( eocn75 == 1 | eocdifference == 0 )

# Linear model incorporating all three treatment effects

# Bottom 25%
summary(lm_robust(
  lrsp ~ eocdifference + post2002 + eocntreat + acres + beds + baths + half_baths + new + age + agesq + year_fe , 
                data = quant_neg_25 , 
                se_type = "stata") )

# Middle 50%
summary(lm_robust(
  lrsp ~ eocdifference + post2002 + eocntreat + acres + beds + baths + half_baths + new + age + agesq + year_fe , 
                data = quant_neg_50 , 
                se_type = "stata") )

# Upper 75%
summary(lm_robust(
  lrsp ~ eocdifference + post2002 + eocntreat + acres + beds + baths + half_baths + new + age + agesq + year_fe , 
                data = quant_neg_75 , 
                se_type = "stata") )

```

## Quantile regressions across house-price distribution

Positively treated houses across 10% quantiles of house-price distribution

```{r}

quant_pos = rq( 
  lrsp ~ rezonepos + post2002 + treatpos + acres + beds + baths + half_baths + new + age + agesq + year_fe ,
  data = treated_pos_df , 
  tau = seq(.1,.9,by=.1) )

summary(quant_pos)

```

Boostrap neighborhood-clustered standard errors across quantile regressions

```{r}

# Specify quantiles
quants = seq(0.1 , 0.9 , by = 0.1)

# Calculate CI bands and store in empty array
qr_array = array(NA , c(nrow = length(quants) , ncol = 2))

for ( i in 1:length(quants) ) {
  qr_b = boot.rq(x = quant_pos$x , y = quant_pos$y , tau = quants[i] , R = 500)
  qr_array[i,] = quantile(qr_b$B[,4] , probs = c(.025,.975) )
}

qr_array

```


```{r}

quant_neg = rq( 
  lrsp ~ rezoneneg + post2002 + treatneg + acres + beds + baths + half_baths + new + age + agesq + year_fe ,
  data = treated_neg_df , 
  tau = seq(.1,.9,by=.1) )

quant_neg

```

```{r}

# Specify quantiles
quants = seq(0.1 , 0.9 , by = 0.1)

# Calculate CI bands and store in empty array
qr_array = array(NA , c(nrow = length(quants) , ncol = 2))

for ( i in 1:length(quants) ) {
  qr_b = boot.rq(x = quant_neg$x , y = quant_neg$y , tau = quants[i] , R = 500)
  qr_array[i,] = quantile(qr_b$B[,4] , probs = c(.025,.975) )
}

qr_array

```






